\plaintitle

### 2025-04-27 docs/style/article-body.tex
minor correction
first tabel, updated teensy makefile

\section{1 INTRODUCTION}\label{introduction}

@@

\subsection{2 THEORY}\label{theory}

@@

\subsubsection{2.1 Shot noise quantum fluctuations}\label{shot-noise-quantum-fluctuations}

@@

\subsection{3 BACKGROUND}\label{background}

@@

\subsubsection{3.1 Optical RNG module}\label{optical-rng-module}

@@

\subsubsection{3.2 ADC converter}\label{adc-converter}

@@

\subsubsection{3.3 Microcontroller}\label{microcontroller}

@@

\subsubsection{\texorpdfstring{3.4 Toeplitz extraction }{3.4 Toeplitz extraction }}\label{toeplitz-extraction}

@@

To summarize the theoretical working of Toeplitz extraction (as explained by Chouhan et al. \cite{toeplitz-desc}), the sampled raw bit matrix (\(T\)) is multiplied with a pre-determined seed matrix (\(K\)). The size of the seed is directly dependent on the size of the sampled data, and can be fixed or continually re-sampled as needed. To ensure high levels of entropy, our intuition is that re-sampling the seed from the OQRNG-device continually is prudent. The sample and seed with then be processed with matrix multiplication to remove deterministic patterns, and produce a bitstring that results in our randomly generated number. An example of how this extraction works can be seen below.

@@

\subsubsection{3.5 Summary}\label{summary}

@@

\subsection{\texorpdfstring{4 RELATED WORKS }{4 RELATED WORKS }}\label{related-works}

@@

\subsection{5 METHODOLOGY}\label{methodology}

@@

\subsubsection{5.1 Iterative approach}\label{iterative-approach}

@@

\subsubsection{5.2 Evaluation}\label{evaluation}

@@

\subsubsection{5.2 Limitations}\label{limitations}

@@

\subsection{6 EXPERIMENTATION}\label{experimentation}

@@

@@

\subsection{CHANGELOG}\label{changelog}

@@

>>>>

\hypertarget{introduction}{%
\section{1 INTRODUCTION}\label{introduction}}

@@

\hypertarget{theory}{%
\subsection{2 THEORY}\label{theory}}

@@

\hypertarget{shot-noise-quantum-fluctuations}{%
\subsubsection{2.1 Shot noise quantum fluctuations}\label{shot-noise-quantum-fluctuations}}

@@

\hypertarget{background}{%
\subsection{3 BACKGROUND}\label{background}}

@@

\hypertarget{optical-rng-module}{%
\subsubsection{3.1 Optical RNG module}\label{optical-rng-module}}

@@

\hypertarget{adc-converter}{%
\subsubsection{3.2 ADC converter}\label{adc-converter}}

@@

\hypertarget{microcontroller}{%
\subsubsection{3.3 Microcontroller}\label{microcontroller}}

@@

\hypertarget{toeplitz-extraction}{%
\subsubsection{\texorpdfstring{3.4 Toeplitz extraction }{3.4 Toeplitz extraction }}\label{toeplitz-extraction}}

@@

To summarize the theoretical working of Toeplitz extraction (as explained by Chouhan et al. \cite{toeplitz-desc}), a pre-determined seed matrix (\(T\)) is multiplied with the sampled raw bit matrix (\(K\)). The size of the seed is directly dependent on the size of the sampled data, and can be fixed or continually re-sampled as needed. To ensure high levels of entropy, our intuition is that re-sampling the seed from the OQRNG-device continually is prudent. The sample and seed with then be processed with matrix multiplication to remove deterministic patterns, and produce a bitstring that results in our randomly generated number. An example of how this extraction works can be seen below.

@@

\hypertarget{summary}{%
\subsubsection{3.5 Summary}\label{summary}}

@@

\hypertarget{related-works}{%
\subsection{\texorpdfstring{4 RELATED WORKS }{4 RELATED WORKS }}\label{related-works}}

@@

\hypertarget{methodology}{%
\subsection{5 METHODOLOGY}\label{methodology}}

@@

\hypertarget{iterative-approach}{%
\subsubsection{5.1 Iterative approach}\label{iterative-approach}}

@@

\hypertarget{evaluation}{%
\subsubsection{5.2 Evaluation}\label{evaluation}}

@@

\hypertarget{limitations}{%
\subsubsection{5.2 Limitations}\label{limitations}}

@@

\hypertarget{experimentation}{%
\subsection{6 EXPERIMENTATION}\label{experimentation}}

@@

For our tests, we used six files with varying degrees of patterns in the bitstring, ranging from quite disastrous to acceptable. We constructed a simple test script to facilitate easier testing of each iteration. This script allowed us to easily test each implementation by automating several tasks -- generating a baseline binary file with data processed by a good, proven implementation of Toeplitz extraction, giving us a way to ensure each iteration still produces the correct result. Furthermore, this script allows us to define different sample sizes for the MCU to utilize, and can extract the amount of time the algorithm takes to execute (\emph{see table 1}) per each sample size.

Below we'll detail the results for each iteration.

@@

\hypertarget{results}{%
\subsection{\texorpdfstring{RESULTS }{RESULTS }}\label{results}}

All iterations was tested on 6 different input datasets, with results variation less than 0.1 microseconds. Thus, they wont be included in tabells unless result is unexpected. All the tables showen below has been tested on ``biased\_bits\_bad''.

Due to compatebility issues, pico pi 2 was tested on different machine, creating some minor variation in result -- about 1 microsecond.

\hypertarget{iteration-1}{%
\subsubsection{Iteration 1}\label{iteration-1}}

\[
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Bit size} & \multicolumn{3}{c|}{\textbf{Teensy (µs)}} & \multicolumn{3}{c|}{\textbf{Pico (µs)}} \\
\hline
& Min & Max & Avg & Min & Max & Avg \\
\hline
64   & 13 & 14 & 13.1564 & 103 & 117 & 106.3914 \\
512  & 788 & 791 & 788.3139 & 5296 & 5311 & 5302.4979 \\
1024 & 3124 & 3130 & 3124.0580 & 21108 & 21119 & 21111.2163 \\
\hline
\end{tabular}
\caption{Minimum, maximum and average processing time for Teensy and Pico.}
\label{tab:teensy_pico_min_max_avg}
\end{table}
\]

\hypertarget{changelog}{%
\subsection{CHANGELOG}\label{changelog}}

@@

2025-04-27: Added first table with test data.
